\newpage
\begin{thebibliography}{50}
  \bibitem{disaster}
  Akram Al-Hourani, Sithamparanathan Kandeepan and Abbas Jamalipour.
  \textit{Stochastic Geometry Study on Device to Device Communication as a Disaster Relief Solution}.
  DOI 10.1109/TVT.2015.2450223, IEEE Transactions on Vehicular Technology.
  
  \bibitem{input}
  Young Jin Chun, Simon L. Cotton, Harpreet S. Dhillon, Ali Ghrayeb and Mazen O. Hasna.
  \textit{A Stochastic Geometric Analysis of Device-to-Device Communications Operating over Generalized Fading Channels}.
  arXiv:1605.03244v1 [cs.IT] 10 May 2016.
  
  \bibitem{interference}
  Moe Z. Win, Pedro C. Pinto, Lawrence A. Shepp.
  \textit{A Mathematical Theory of Network Interference and Its Applications}.
  Vol.97, No.2, February 2009, Proceedings of the IEEE.
  
  \bibitem{ccinter}
  Eric W. Weinsstein
  \textit{Circle-Circle Intersection}.
  MathWorld--A Wolfram Web Resource. http://mathworld.wolfram.com/Circle-CircleIntersection.html
  
  \bibitem{condprob}
  Patrick Billingsley.
  \textit{Probability and Measure, 3\textsuperscript{rd} edition}.
   p.439, New York: John Willey and Sons, 1995.
   
  \bibitem{totprob}
  Deborah Rumsey.
  \textit{Probability for Dummies}.
  p.58, For Dummies, ISBN 978-0-471-75141-0, 2006.

  \bibitem{survey}
  Arash Asadi, Qing Wang, Vincenzo Mancuso
  \textit{A survey on device-to-device communication in cellular networks}
  arXiv:1310.0720v6 [cs.GT], 29 Apr. 2014.
 
  \bibitem {avoidance}
  T.Peng, Q.Lu, H.Wang, S.Xu, W.Wang
  \textit {Interference avoidance mechanisms in the hybrid cellular and device-to-device systems}
  Proceedings of IEEE, PIMRC, 2009, pp.617-621.

  \bibitem {ratesplitting}
  C.-H.Yu, O.Tirkkonen
  \textit {Device-to-device underlay cellular network based on rate splitting}
  Proceedings of IEEE, WCNC, 2012, pp.262-266.

  \bibitem {doppler}
  A.Osseiran, K.Doppler, C.Ribeiro, M.Xiao, M.Skoglund, J.Mansour
  \textit {Advances in device-to-device communications and network coding for IMT-Advanced}
  ICT Mobile Summit, 2009.

  \bibitem {choi}
  M.Jung, K.Hwang, S.Choi
  \textit {Joint mode selection and power allocation scheme for power-efficient device-to-device communication}
  Proceedings of IEEE, VTC-Spring, 2012, pp.1-5.

  \bibitem {kosketa}
  S.Hakola, T.Chen, J.Lehtomaki, T.Koskela
  \textit {Device-to-device communication in cellular network-performance analysis of optimum and practical communication mode selection.}
  Proceedings of IEEE, WCNC, 2010, pp.1-6.

  \bibitem {cognitive}
  P.Cheng, L.Deng, H.Yu, Y.Xu, H.Wang
  \textit {Resource allocation for cognitive networks with D2D communication: an evolutionary approach}
  Proceedings of IEEE, WCNC, 2012, pp.2671-2676.

  \bibitem {milcom}
  K.Vanganuru, S.Ferrante, G.Sternberg
  \textit {System capacity and coverage of a cellular network with D2D mobile relays.}
  Military Communications Conference-MilCom, 2012, pp.1-6.

  \bibitem {dataspotting}
  X.Bao, U.Lee, I.Rimac, R.Choudhury
  \textit {DataSpotting: offloading cellular traffic via managed device-to-device data transfer at data spots}
  ACM SIGMOBILE Mobile computing and communications review, 2010, vol.14, no.3, pp.37-39.

  \bibitem {mumimo}
  J.C.Li, M.Lei, F.Gao
  \textit {Device-to-device communication in MU-MIMO cellular netowrks}
  Proceedings of IEEE, GLOBECOM, 2012, pp.3583-3587

  \bibitem {intra}
  B.Zhou, H.Hu, S.-Q.Huang, H.-H.Chen
  \textit {Intracluster device-to-device relay algorithm with optimal resource utilization}
  IEEE transactions on Vehicular Technology, Jun.2013, vol.62, no.5, pp.2315-2326
 
  \bibitem {asadi}
  A.Asadi, V.Mancuso
  \textit {Energy efficient opportunistic uplink packet forwarding in hybrid wireless netowrks.}
  Proceedings of the 4\textsuperscript{th} international conference on future energy systems, 2013, pp.261-262.

  \bibitem {mancuso}
  A.Asadi, V.Mancuso
  \textit {On the compound impact of opportunistic scheduling and D2D communications in cellular networks.}
  ACM MSWIM, 2013.

  \bibitem {caching}
  M.Ji, G.Caire, A.Molisch
  \textit {Wireless device-to-device caching networks: basic principles and system performance.}
  arXiv:1305.5216, 2013.

\end{thebibliography}
